Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-06-02 manuscript.Rmd
figures export to png

There are differences between modern and fossil grains (Fig. \@ref(fig:meanDAL), \@ref(fig:meanMFM) and \@ref(fig:meanTSK).
The prominent and characteristic sporopollenin peaks (1600, 1510 and 1170 cm^-1^) are visible in the fossil pollen, while other parts of the spectra show substantial differences.
Most notibly the lipid peak at 1745 cm^-1^, caused by triglycerides, is not visible in the fossil pollen grains, neither in the SPT treated or acetolysed pollen.
There are also several differences in the "fingerprint" region (1500 to 1800 cm^-1^) and carbohydrate region from 1000 to 1250 cm^-1^ between modern and fossil pollen grains.
A peak at 1030 and ~1200 cm^-1^ is visible in the acetolysed pollen but not in the modern spectra, while we see a broad peak at 1090-1100 cm^-1^ in the SPT spectra of all three cores.
This peak is not present in either modern pollen or acetolysed pollen, additionally Tiefer See shows a similar peak at 1630.

@@

the peak at 1170 cm^-1^ is more pronounced in spt than acetolyzed pollen.

@@

```{r meanFRE, echo=FALSE, fig.cap="FRE", message=FALSE, warning=FALSE, out.width="100%"}
mean_plotsSM = readRDS(here("data","output","mean_plots.rds"))

mean_plotsSM[[7]]
```

```{r meanDAL, echo=FALSE, fig.cap="DAL whole core mean plots", message=FALSE, warning=FALSE, out.width="100%"}
mean_plots = readRDS(here("data","output","mean_plots_whole.rds"))

mean_plots[[1]]
```

```{r meanMFM, echo=FALSE, fig.cap="MFM whole core mean plots", message=FALSE, warning=FALSE, out.width="100%"}
mean_plots[[2]]
```

```{r meanTSK, echo=FALSE, fig.cap="TSK whole core mean plots", message=FALSE, warning=FALSE, out.width="100%"}
mean_plots[[3]]
```

@@

# Mean spectra figures SM

>>>>

There are differences between modern and fossil grains (Fig. \@ref(fig:meanDAL), \@ref(fig:meanMFM) and \@ref(fig:meanTSK).
The prominent and characteristic sporopollenin peaks (1600, 1510 and 1170 cm^-1^) are visible in the fossil pollen, while other parts of the spectra show substantial differences.
Most notibly the lipid peak at 1745 cm^-1^, caused by triglycerides, is not visible in the fossil pollen grains, neither in the SPT treated or acetolysed pollen.
There are also several differences in the "fingerprint" region (1500 to 1800 cm^-1^) and carbohydrate region from 1000 to 1250 cm^-1^ between modern and fossil pollen grains.

@@

A peak at 1030 and ~1200 cm^-1^ is visible in the acetolysed pollen but not in the modern spectra or SPT pollen.
We see a broad peak at 1090-1100 cm^-1^ in the SPT spectra of all three cores.
This peak is not present in either modern pollen or acetolysed pollen, additionally Tiefer See shows a similar peak at 1630.

@@

```{r meanspectra, echo=FALSE, fig.cap="FRE", message=FALSE, warning=FALSE, out.width="100%"}
knitr::include_graphics(here("figures", "mean_plots.png"))

mean_plotsSM = readRDS(here("data","output","mean_plots.rds"))
mean_plots = readRDS(here("data","output","mean_plots_whole.rds"))
```

```{r ordinations, echo=FALSE, fig.cap="FRE", message=FALSE, warning=FALSE, out.width="100%"}
knitr::include_graphics(here("figures", "ord_plots.png"))
```

@@

\newpage
\newpage
# Mean spectra figures SM
